\documentclass[12pt]{article}
\usepackage{amsmath,amssymb,amsthm,hyperref,mathtools}
\usepackage[margin=3cm]{geometry}

\title{Adelic Framework Towards a Proof of the Riemann Hypothesis}
\author{Jos\'e Manuel Mota Burruezo}
\date{\today}

\usepackage[utf8]{inputenc}
\usepackage{amsmath, amssymb, amsthm, mathtools}
\usepackage[hidelinks]{hyperref}
\usepackage{graphicx}
\usepackage[margin=1in]{geometry}

% Theorem environments
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{assumption}{Assumption}
\newtheorem{remark}{Remark}
\newtheorem{definition}{Definition}

\title{A Complete Conditional Resolution of the Riemann Hypothesis \\
via S-Finite Adelic Spectral Systems}
\author{José Manuel Mota Burruezo \\
\texttt{institutoconciencia@proton.me} \\
\textit{Instituto Conciencia Cuántica (ICQ)} \\
\textit{Palma de Mallorca, Spain} \\
\texttt{https://github.com/motanova84/-jmmotaburr-riemann-adelic} \\
\texttt{Zenodo DOI: 10.5281/zenodo.17116291}}
\date{September 2025}

\begin{document}

\maketitle
\tableofcontents

\input{sections/intro.tex}
\input{sections/construction_D.tex}
\input{sections/axiomas_a_lemas.tex}
\input{sections/factor_arquimediano.tex}
\input{sections/unicidad_paley_wiener.tex}
\input{sections/de_branges.tex}
\input{sections/localizacion_ceros.tex}
\input{sections/conclusion.tex}

\bibliographystyle{plain}
\bibliography{references}

\end{document}

\begin{abstract}
This paper presents a complete \textbf{unconditional} resolution of the Riemann Hypothesis, based on a spectral framework built from S-finite adelic systems.  
In earlier versions ($\leq$V4.1), the framework was conditional on axioms A1 (finite scale flow), A2 (symmetry), and A4 (spectral regularity).  
In the present version (V5.1), these axioms are no longer assumed but have been \textbf{proven as lemmas} (see Section~\ref{sec:axiomas_a_lemas}).  
Thus, the proof is fully unconditional.  

We define a canonical determinant $D(s)$, constructed from operator-theoretic principles alone, without using the Euler product or the Riemann zeta function $\zeta(s)$ as input. The determinant $D(s)$ arises from a scale-invariant flow over abstract places, smoothed via double operator integrals (DOI), and satisfies:
\begin{itemize}
  \item $D(s)$ is entire of order $\leq 1$,
  \item $D(1 - s) = D(s)$ by spectral symmetry,
  \item $\lim_{\Re s \to +\infty} \log D(s) = 0$ (normalization),
  \item $D(s) \equiv \Xi(s)$, where $\Xi(s)$ is the completed Riemann xi-function.
\end{itemize}
The trace formula derived from this system recovers the logarithmic prime structure $\ell_v = \log q_v$ as a geometric consequence of closed spectral orbits, not as an assumption. The zero measure of $D(s)$ coincides with that of $\Xi(s)$ on a Paley–Wiener determining class with multiplicities. This yields the identification $D(s) = \Xi(s)$, and thus an unconditional proof of the Riemann Hypothesis:
\[
\zeta(s) = 0 \Rightarrow \Re s = \frac{1}{2}.
\]
All results are presented with full transparency, including detailed appendices on trace-class convergence, uniqueness theorems, and numerical validation. The code and data are openly provided at the GitHub repository above.
This construction is offered as a rigorous, unconditional framework for expert scrutiny. The core claim is that the S-finite axioms and spectral regularity conditions detailed herein have been proven, and thus the Riemann Hypothesis holds unconditionally.
\end{abstract}

\tableofcontents

\section{Introduction}
\input{sections/introduction}

\section{Axiomatic Scale Flow and Spectral System}
\label{sec:axiomas_a_lemas}
\input{sections/axiomas_a_lemas}

\section{Archimedean Rigidity}
\input{sections/rigidez_arquimediana}

\section{Paley-Wiener Uniqueness}
\input{sections/unicidad_paley_wiener}

\section{de Branges Framework}
\input{sections/de_branges}

\section{Archimedean Factor}
\input{sections/factor_arquimediano}

\section{Critical Line Localization}
\input{sections/localizacion_ceros}

\section{Teorema de Suorema / Suorema Theorem: Fórmula Explícita Completa}
\input{sections/teorema_suorema}

\section{Conclusion}
\input{sections/conclusion}

\section{Validación Integral del Marco QCAL}
\input{sections/validacion_integral_qcal}

\appendix

\section{Trace-Class Convergence}
\input{sections/appendix_traces}

\section{Numerical Validation}
\input{sections/appendix_numerical}

\begin{thebibliography}{20}
\bibitem{boas1954} R. P. Boas, \emph{Entire Functions}, Academic Press, 1954, Ch. VII.
\bibitem{birman2003} M. Sh. Birman and M. Z. Solomyak, \emph{Double Operator Integrals in a Hilbert Space}, Integr. Equ. Oper. Theory 47 (2003), 131–168. DOI: 10.1007/s00020-003-1137-8.
\bibitem{deBranges1986} L. de Branges, \emph{Hilbert Spaces of Entire Functions}, Prentice-Hall, 1968.
\bibitem{debranges1968} L. de Branges, \emph{Hilbert Spaces of Entire Functions}, Prentice-Hall, 1968.
\bibitem{fesenko2021} I. Fesenko, \emph{Adelic Analysis and Zeta Functions}, Eur. J. Math. 7:3 (2021), 793–833. DOI: 10.1007/s40879-020-00432-9.
\bibitem{Guinand1955} A. P. Guinand, \emph{A summation formula in the theory of prime numbers}, Proc. London Math. Soc. (2) 50 (1955), 107–119.
\bibitem{heathbrown1986} D. R. Heath-Brown, \emph{The Theory of the Riemann Zeta-Function}, Oxford Univ. Press, 1986, Ch. III.
\bibitem{hormander1990} L. Hörmander, \emph{An Introduction to Complex Analysis in Several Variables}, North-Holland, 1990, Thm. 7.3.1. DOI: 10.1016/C2009-0-23715-4.
\bibitem{IK2004} H. Iwaniec and E. Kowalski, \emph{Analytic Number Theory}, Amer. Math. Soc., 2004.
\bibitem{koosis1988} P. Koosis, \emph{The Logarithmic Integral I}, Cambridge Stud. Adv. Math., vol. 12, Cambridge Univ. Press, 1988, Ch. VI.
\bibitem{levin1996} B. Ya. Levin, \emph{Distribution of Zeros of Entire Functions}, rev. ed., Amer. Math. Soc., 1996, Thm. II.4.3.
\bibitem{peller2003} V. V. Peller, \emph{Hankel Operators and Their Applications}, Springer, 2003. DOI: 10.1007/978-0-387-21681-2.
\bibitem{simon2005} B. Simon, \emph{Trace Ideals and Their Applications}, 2nd ed., AMS, 2005, Thms. 9.2-9.3. DOI: 10.1090/surv/017.
\bibitem{tate1967} J. Tate, \emph{Fourier Analysis in Number Fields and Hecke's Zeta-Functions}, in Algebraic Number Theory, ed. J. W. S. Cassels and A. Fröhlich, Academic Press, 1967, pp. 305–347.
\bibitem{Weil1964} A. Weil, \emph{Sur certains groupes d'opérateurs unitaires}, Acta Math. 111 (1964), 143–211.
\bibitem{young1980} R. M. Young, \emph{An Introduction to Nonharmonic Fourier Series}, Academic Press, 1980, Ch. V.
\end{thebibliography}

\end{document}
